### 2010-12-14 docs/tex/intro.tex
Introduction

%A few paragraphs are required to bring an appropriate introduction.
%Throughout history mankind has learned from nature. Human aspiration to fly in the sky comes from observing birds in the sky. Aspiration leads to inspiration, and airplanes are invented.

>>>>

%A few paragraphs are required to bring an appropriate introduction.
Mimicry is a process of deception. It is an evolutionary process with the help of which organisms survive by deceiving its predator. But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable. Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.

Artificial Life is an interdisciplinary study of life and life-like processes that uses synthetic methodology. This thesis consists of such a work which concentrates specifically on the life-like process of the evolution of mimicry. The synthetic tools used for this simulation is a three dimensional graphical environment, Cellular Automata and Neural Network.
